Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-03-26 papers/intro_paper/intro.tex
changes in Sec. I

The LIGO-Virgo collaborations have released companion papers detailing their results
of tests of GR for GW150914 \cite{TheLIGOScientific:2016src}, and for several GW events of
the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
The results include tests of GW generation and source dynamics, where bounds are placed on
parameterized deviations in the post-Newtonian (PN) coefficients describing
the early inspiral, and
phenomenological coefficients describing the intermediate (plunge) and
merger regimes of coalescence~\cite{Arun:2006hn,Arun:2006yw,Agathos:2013upa,Abbott:2018lct}; tests of GW
propagation, which assume a generalized dispersion relation and place
upper bounds on the Compton wavelength and, consequently, the mass of
the graviton~\cite{Abbott:2017vtc,Samajdar:2017mka}, and tests of the
polarization of gravitational radiation using a
multi--GW-detector network~\cite{Abbott:2017oio,Isi:2017fbj}. The GWTC-1/2 papers also
check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
consistency of the residuals with \abhi{detector}
noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
departure from the predictions of GR.

@@

The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
we apply our method on real GW events \abhi{in} LIGO and Virgo data. In particular, we analyze
the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
our results and discuss future developments.

>>>>

The LIGO-Virgo collaborations have released companion papers detailing their results
of tests of GR for GW150914 \cite{TheLIGOScientific:2016src}, and for several GW events of
the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
The results include tests of GW generation and source dynamics, where bounds are placed on
parameterized deviations in the post-Newtonian (PN) coefficients describing
the early inspiral, and
phenomenological coefficients describing the intermediate (plunge) and
merger regimes of coalescence~\cite{Arun:2006hn,Arun:2006yw,Agathos:2013upa,Abbott:2018lct}; tests of GW
propagation, which assume a generalized dispersion relation and place
upper bounds on the Compton wavelength and, consequently, the mass of
the graviton~\cite{Abbott:2017vtc,Samajdar:2017mka}, and tests of the
polarization of gravitational radiation using a
multi--GW-detector network~\cite{Abbott:2017oio,Isi:2017fbj}. The GWTC-1/2 papers also
check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
consistency of the residuals with detector noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
departure from the predictions of GR.

@@

The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
our results and discuss future developments.
